---
title: "shannon_exploration"
output: html_document
---

# Import libaries
```{r}
library(tidyverse)
library(ggplot2)
library(lubridate)
```

# Read data
```{r}
wego <- read_csv("../data/Route 50 Timepoint and Headway Data, 1-1-2023 through 5-12-2025.csv")

# Display head
wego |> 
  slice_head(n = 5)
```

# Create columns
```{r}
wego <- wego |> 
  mutate(TSP_STATUS = 0, .before = CALENDAR_ID) |> 
  mutate(DAY_OF_WEEK = weekdays(DATE), .after = DATE) |> 
  mutate(WEEKEND = case_when(DAY_OF_WEEK %in% c("Saturday", "Sunday") ~ 1, .default = 0), .after = DAY_OF_WEEK)

# Display head
wego |> 
  slice_head(n = 1)
```

# Convert timestamp columns
```{r}
wego <- wego |> 
  mutate(SCHEDULED_HMS = hms(str_sub(SCHEDULED_TIME, start = -8L, end = -1L)), .after = SCHEDULED_TIME) |> 
  mutate(ACTUAL_ARRIVAL_HMS = hms(str_sub(ACTUAL_ARRIVAL_TIME, start = -8L, end = -1L)), .after = ACTUAL_ARRIVAL_TIME) |> 
  mutate(ACTUAL_DEPARTURE_HMS = hms(str_sub(ACTUAL_DEPARTURE_TIME, start = -8L, end = -1L)), .after = ACTUAL_DEPARTURE_TIME) |> 
  arrange(ACTUAL_DEPARTURE_HMS)

# Display head
wego |> 
  slice_head(n = 1)
```

# Update TSP_STATUS for February 3rd @ 12 noon: TSP Turned On (Unconditional)

```{r}
wego <- wego |> 
  # FROM DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-03" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG")
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-03" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46")
                        ),
                      values = 1
                    )
  )

wego |> 
  filter(DATE == "2025-02-03" & TSP_STATUS == 1)
```

# Update TSP_STATUS for February 10th @ 12 noon: TSP Schedule-Conditional Priority Begins (Only buses more than 2 minutes late receive priority)

```{r}
wego <- wego |> 
  # FROM DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-10" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG")
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-10" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46")
                        ),
                      values = 1
                    )
  )

wego |> 
  filter(DATE == "2025-02-10" & TSP_STATUS == 1)
```

# Update TSP_STATUS for April 28th @ 12 noon: TSP Turned Off
```{r}
wego <- wego |> 
  # FROM DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-04-28" & 
                          ACTUAL_DEPARTURE_HMS < hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG")
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-04-28" & 
                          ACTUAL_DEPARTURE_HMS < hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46")
                        ),
                      values = 1
                    )
  )

wego |> 
  filter(DATE == "2025-04-28" & TSP_STATUS == 1)
```

# Update TSP_STATUS for May 5th @ 12 noon: TSP Turned On (Unconditional)

```{r}
wego <- wego |> 
  # FROM DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-05-05" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG")
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-05-05" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46")
                        ),
                      values = 1
                    )
  )

wego |> 
  filter(DATE == "2025-05-05" & TSP_STATUS == 1)
```

# Update TSP_STATUS for May 12th @ 12 noon: TSP Headway-Conditional TSP Priority Begins (Only gapped buses with actual leading headway more than 120% of scheduled headway receive priority)

```{r}
wego <- wego |> 
  # FROM DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-05-12" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG")
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-05-12" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46")
                        ),
                      values = 1
                    )
  )

wego |> 
  filter(DATE == "2025-05-12" & TSP_STATUS == 1)
```

```{r}
wego |> 
  filter(TSP_STATUS == 1)
```

# Create a binary logistic regression model for ADJUSTED_LATE_COUNT with TSP_STATUS
```{r}
adj_late_tsp_lrm = glm(ADJUSTED_LATE_COUNT ~ TSP_STATUS, data = wego, family = "binomial")

summary(adj_late_tsp_lrm)
```

```{r}
adj_late_tsp_predict <- predict(
    adj_late_tsp_lrm,
    newdata = data.frame(
      TSP_STATUS = c(1, 0)
    ),
    type = "response"
  )

adj_late_tsp_predict
```

# Create logistic regression model for ADJUSTED_LATE_COUNT with TSP_STATUS and DAY_OF_WEEK
```{r}
adj_late_tsp_dywk_lrm = glm(ADJUSTED_LATE_COUNT ~ TSP_STATUS + DAY_OF_WEEK, data = wego, family = "binomial")

summary(adj_late_tsp_dywk_lrm)
```

# Probability of being late when TSP is turned for each day of the week
```{r}
predict(
  adj_late_tsp_dywk_lrm,
  newdata = data.frame(TSP_STATUS = 1, DAY_OF_WEEK = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")),
  type = "response"
)
```

# Probability of being late when TSP is turned off for each day of the week
```{r}
predict(
  adj_late_tsp_dywk_lrm,
  newdata = data.frame(TSP_STATUS = 0, DAY_OF_WEEK = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")),
  type = "response"
)
```
# Create logistic regression model for ADJUSTED_LATE_COUNT with TSP_STATUS and WEEKEND
```{r}
adj_late_tsp_wkend_lrm = glm(ADJUSTED_LATE_COUNT ~ TSP_STATUS + WEEKEND, data = wego, family = "binomial")

summary(adj_late_tsp_wkend_lrm)
```

# Probability of being late when TSP is turned on/off during the weekend
```{r}
predict(
  adj_late_tsp_wkend_lrm,
  newdata = data.frame(TSP_STATUS = c(1, 0), WEEKEND = 1),
  type = "response"
)
```

# Probability of being late when TSP is turned on/off during the workweek
```{r}
predict(
  adj_late_tsp_wkend_lrm,
  newdata = data.frame(TSP_STATUS = c(1, 0), WEEKEND = 0),
  type = "response"
)
```

# Create logistic regression model for ADJUSTED_LATE_COUNT with TSP_STATUS for just 2025
```{r}
wego_2025 <- wego |> 
  filter(year(DATE) == 2025)
```

```{r}
adj_late_tsp_2025_lrm = glm(ADJUSTED_LATE_COUNT ~ TSP_STATUS, data = wego_2025, family = "binomial")

summary(adj_late_tsp_2025_lrm)
```

# Probability of being late when TSP is turned on/off in 2025
```{r}
predict(
  adj_late_tsp_2025_lrm,
  newdata = data.frame(TSP_STATUS = c(1, 0)),
  type = "response"
)
```

# Create logistic regression model for ADJUSTED_LATE_COUNT with TSP_STATUS for same timeframe year over year
```{r}
dates <- c(date("2025-04-28"), date("2025-05-05"), date("2025-02-03"), date("2025-05-12"), date("2025-02-10"))

wego_yr_over_yr <- wego |> 
  filter(month(DATE) == month(dates) & day(DATE) == day(dates))
```

```{r}
adj_late_tsp_yroveryr_lrm = glm(ADJUSTED_LATE_COUNT ~ TSP_STATUS, data = wego_yr_over_yr, family = "binomial")

summary(adj_late_tsp_yroveryr_lrm)
```

# Probability of being late when TSP is turned on/off year over year
```{r}
predict(
  adj_late_tsp_yroveryr_lrm,
  newdata = data.frame(TSP_STATUS = c(1, 0)),
  type = "response"
)
```

# Model with WEEKDAY
# YEAR (2025)
# YEAR OVER YEAR