---
title: "shannon_exploration"
output: html_document
---

# Import libaries
```{r}
library(tidyverse)
library(lubridate)
```

# Read data
```{r}
wego <- read_csv("../data/Route 50 Timepoint and Headway Data, 1-1-2023 through 5-12-2025.csv")

# Display head
wego |> 
  slice_head(n = 5)
```

# Create TSP_STATUS column
```{r}
wego <- wego |> 
  mutate(TSP_STATUS = 0, .before = CALENDAR_ID)

# Display head
wego |> 
  slice_head(n = 1)
```

# Convert timestamp columns
```{r}
wego <- wego |> 
  mutate(SCHEDULED_HMS = hms(str_sub(SCHEDULED_TIME, start = -8L, end = -1L)), .after = SCHEDULED_TIME) |> 
  mutate(ACTUAL_ARRIVAL_HMS = hms(str_sub(ACTUAL_ARRIVAL_TIME, start = -8L, end = -1L)), .after = ACTUAL_ARRIVAL_TIME) |> 
  mutate(ACTUAL_DEPARTURE_HMS = hms(str_sub(ACTUAL_DEPARTURE_TIME, start = -8L, end = -1L)), .after = ACTUAL_DEPARTURE_TIME) |> 
  arrange(ACTUAL_DEPARTURE_HMS)

# Display head
wego |> 
  slice_head(n = 1)
```

# Update TSP_STATUS for February 3rd @ 12 noon: TSP Turned On (Unconditional)

```{r}
wego <- wego |> 
  # FROM DOWNTOWN (153)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-03" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG")
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN (108)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-03" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46")
                        ),
                      values = 1
                    )
  )
```

# Update TSP_STATUS for February 10th @ 12 noon: TSP Schedule-Conditional Priority Begins (Only buses more than 2 minutes late receive priority)

```{r}
wego <- wego |> 
  # FROM DOWNTOWN (39)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-10" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG") &
                          ADHERENCE <= -2.0
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN (45)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-10" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46") &
                          ADHERENCE <= -2.0
                        ),
                      values = 1
                    )
  )
```

# Update TSP_STATUS for April 28th @ 12 noon: TSP Turned Off
```{r}
wego <- wego |> 
  # FROM DOWNTOWN (93)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-28" & 
                          ACTUAL_DEPARTURE_HMS < hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG")
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN (74)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-02-28" & 
                          ACTUAL_DEPARTURE_HMS < hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46")
                        ),
                      values = 1
                    )
  )
```

# Update TSP_STATUS for May 5th @ 12 noon: TSP Turned On (Unconditional)

```{r}
wego <- wego |> 
  # FROM DOWNTOWN (152)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-05-05" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG")
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN (112)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-05-05" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46")
                        ),
                      values = 1
                    )
  )
```

# Update TSP_STATUS for May 12th @ 12 noon: TSP Headway-Conditional TSP Priority Begins (Only gapped buses with actual leading headway more than 120% of scheduled headway receive priority)

```{r}
wego <- wego |> 
  # FROM DOWNTOWN (18)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-05-12" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "FROM DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG") &
                          ACTUAL_HDWY >= SCHEDULED_HDWY * 1.2
                        ),
                      values = 1
                    )
  ) |> 
  # TO DOWNTOWN (21)
  mutate(
      TSP_STATUS = replace(
                      x = TSP_STATUS,
                      list = (
                          DATE == "2025-05-12" & 
                          ACTUAL_DEPARTURE_HMS >= hms("12:00:00") &
                          ROUTE_DIRECTION_NAME == "TO DOWNTOWN" &
                          TIME_POINT_ABBR %in% c("MCC5_1", "28&CHARL", "CH46", "WHBG") &
                          ACTUAL_HDWY >= SCHEDULED_HDWY * 1.2
                        ),
                      values = 1
                    )
  )
```

